Fixing Vulnerabilities Hinders Maintainability

### 2019-01-30 paper/ICPC19/icpc19.tex
main contributions

In this paper, we present the results of our analysis on the maintainability of 607 security changes collected from open-source software. The main contributions of the present work is an empirical study on the impact of security changes on software maintainability and what patterns need more attention. This empirical study exhibits proof that changes applied in the codebase to fix vulnerabilities affect code maintainability. Especially, for refactorings that address \emph{Broken Authentication and Session Management} issues, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. With this study, we intend to highlight the need for tools and documentation to help developers 
adopt security best practices.

>>>>

In this paper, we present the results of our analysis on the maintainability of 607 security changes collected from open-source software.

The main contributions of the present work is:
\begin{itemize}
	\item An empirical study on the impact of security changes on software maintainability and what patterns need more attention.
	\item A software package with all scripts and data created to perform the empirical evaluation, for reproducibility. Available here: $<url>$.

\end{itemize}

This empirical study exhibits proof that changes applied in the codebase to fix vulnerabilities affect code maintainability. Especially, for refactorings that address \emph{Broken Authentication and Session Management} issues, \emph{Memory Leaks} and \emph{Denial-of-Service} attacks. With this study, we intend to highlight the need for tools and documentation to help developers 
adopt security best practices.
